---
title: "MT4113 - Report"
author: '180024570'
date: "07/11/2018"
output:
  pdf_document:
    extra_dependencies: subfig
    fig_caption: yes
    includes: null
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
header-includes:
 \usepackage{booktabs}
 \usepackage{longtable}
 \usepackage{array}
 \usepackage{enumitem} 
 \usepackage{multirow}
 \usepackage[table]{xcolor}
 \usepackage{wrapfig}
 \usepackage{float}
 \floatplacement{figure}{H}
 \usepackage[bottom]{footmisc}
bibliography: reference.bib
csl: harvard.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE)

library(dslabs)
library(dplyr)
library(knitr)
library(kableExtra)
```

*I conﬁrm that the following report and associated code is my own work, except where clearly indicated.*


\newpage

# Abstract

More than 17 million people voted to leave the EU in 2016 Referendum in the UK. This statistical report investigated the difference of approval rates of Brexit in England and the rest of the UK by carrying out both parametric and non-parametric tests. Particularly, Monte Carlo simulation is conducted on the referendum dataset by regions, to research the properties of those statistical tests under a range of different scenarios. *add a bit summary of result*

# Introduction

Hundreds of thousands of people marched to London's Parliament Square for a referendum on the final Brexit deal in late October[@BBCNews2018]. In the EU referendum in 2016, approximately 52%, or more than 17 million people in the UK, voted to leave the European Union [@Becker2017]. To investigate what voters in different nations of the UK vote for, the dataset of EU referendum results by regions[@ElectoralCommission2016] are statistically analysed and tested in this report.

```{r}

```


The research question is

**Were approval rates of Brexit greater in England or rest of the UK in 2016 referendum?**


# Methodology



# Result and Discussion

```{r size-tables}
load("../data/3.RData")

header <- c(group1 = 1, group2 = 5, group3 = 5)
names(header) <- c("Sample Size","SD Difference","SD Difference(record round to 0)")
kable(siz, caption = "Size of Student's T Test", booktabs=T) %>% 
  add_header_above(header = header, bold = TRUE)

header <- c(group1 = 1, group2 = 5, group3 = 5)
names(header) <- c("Sample Size","SD Difference","SD Difference(record round to 0)")
kable(sizNonPar, caption = "Size of Mann-Whitney U Test", booktabs=T) %>% 
  add_header_above(header = header, bold = TRUE)

```


# Conclusion

# Reference

# Appendix